The Driving Forces Behind API Evolution

### 2015-05-20 thesis/paper.tex
disc rq2

\subsection{RQ2 Answer}
Based on the results

%1.1 Give a clear answer to the RQ. (Reject null / alternative)

%1.2 Point to results
%      -Bring up the most interesting/distinct trends

%1.3 Compare to literature (i.e. relate to previous work)
 %      -Do our results agree with prev. work?

>>>>

\subsection{RQ2 Answer}
We conclude that we were able to reverse engineer the change decisions to a large extent. This is clear from the results, which showed that 85\% of the changes were reverse engineered correctly. The kappa value of 0.812 further supports this. We interpret that the significance of this result suggests that reverse engineering of change decisions can be done in situations where a perfect result is not required. In cases where a near-perfect result is enough, we do, however, believe that reverse engineering change decisions is worthwhile (!!!this sentence weird). This line of thought is supported by our results, which, in summary, show that we are able to reverse engineer the most major trends with very high accuracy, but that certain nuances of the changes can be misinterpreted.
